%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\include{macro}	% マクロを読み込む

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage[dvipdfmx]{hyperref}

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Naoya Muramatsu}	% Your name
\address{mrmnao001@myuct.ac.za}	% Your phone number and email
\address{sh.mn.nat@gmail.com}	% Your phone number and email
% \address{Yashio, Saitama Pref., Japan}	% Your address
% \address{123 Pleasant Lane \\ City, State 12345} % Your secondary address (optional)


\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

    \begin{rSubsection}{University of Cape Town}{April 2021 -- Present}{PhD student in Electrical Engineering}{}
    % New type of deep learning
    \item On the Neuromechanics of the Cheetah.
    \item Adviser: \href{https://scholar.google.co.za/citations?user=RxMigV4AAAAJ&view_op=list_works&sortby=pubdate}{Amir Patel}
    \end{rSubsection}

    \begin{rSubsection}{University of Tsukuba}{April 2018 -- March 2021}{MSc in Information Science}{}
    % New type of deep learning
    \item Dissertation title: ``{\it SNN Meets ANN: Combining Spiking Neural Network (SNN) and Artificial Neural Network (ANN) for Image Classification}''
    \item Adviser: \href{http://www.slis.tsukuba.ac.jp/~satoh.tetsuji.gf/index.html}{Tetsuji Satoh}
    \item Subadviser: \href{https://scholar.google.co.jp/citations?user=88b2NRsAAAAJ&hl=ja}{Hai-Tao Yu}
    \end{rSubsection}

    \begin{rSubsection}{University of Tsukuba}{April 2016 -- March 2018}{BSc in Library and Information Science}{}
    \item Dissertation title: ``{\it Deep Learning in Reciprocal Lattice Space}''
    \item Adviser: \href{https://scholar.google.co.jp/citations?user=obhH0jkAAAAJ&hl=en}{Yoichi Ochiai}
    \end{rSubsection}

    \begin{rSubsection}{National Institute of Technology, Nagano College}{April 2015 -- March 2016}{Foundation Degree}{}
    \item Dissertation title: ``{\it Indoor location acquisition using a power-saving wireless network}''(省電力無線ネットワークを用いた屋内位置情報取得)
    \item Adviser: \href{https://researchmap.jp/read0178034?lang=en}{Takashi Miyazaki}
    \end{rSubsection}

\end{rSection}

\begin{rSection}{Industrial Experience}

    \begin{rSubsection}{\href{https://info.gbiz.go.jp/hojin/ichiran?hojinBango=2430001082637}{Good Answers, Inc.}}{February 2021 -- Present}{Fellow}{}
    \item Developing the motor control algorithm for electric scooters.
    \end{rSubsection}

    \begin{rSubsection}{\href{https://www.landscape.co.jp/}{Landscape Co.,Ltd.}}{January 2020 -- Present}{Outside CTO}{}
    \item Working on developing systems with Machine Learning techniques, such as optical character recognition and image recognition.
    \end{rSubsection}

    \begin{rSubsection}{Information-technology Promotion Agency, Japan. Exploratory Software Project (\href{https://www.mitou.org/}{MITOU})}{June 2018 -- March 2019}{Creator}{}
    \item Developed the robot control system, walking even with broken legs using hierarchy Q-learning.
    \item \textbf{2,304,000 JPY / nine months}.
    \end{rSubsection}

    \begin{rSubsection}{\href{http://pixiedusttech.com/}{Pixie Dust Technologies, Inc.}}{August 2017 -- April 2019}{Software Engineer}{}
    \item Worked on the development of management systems and web applications.
    \end{rSubsection}

    \begin{rSubsection}{\href{https://www.fixstars.com/en/}{Fixstars Corporation}}{August 2016 -- December 2016}{Software Engineer Intern}{}
    \item Worked on the development of a semantic segmentation system for self-driving cars.
    \end{rSubsection}

    \begin{rSubsection}{\href{https://www.fixstars.com/en/}{Fixstars Corporation}}{August 2014 -- September 2014}{Software Engineer Intern}{}
    \item Worked on software optimisation for the microcomputer of cars.
    \end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Publications} \itemsep 4pt

    % \begin{rSubsection}{Preprints}{}{}{}{}
    %     % arxivとか
    % \end{rSubsection}

    \begin{rSubsection}{JOURNALS}{}{}{}{}
        \item \textbf{Naoya Muramatsu}*, Hai-Tao Yu, Tetsuji Satoh, "Combining Spiking Neural Networks with Artificial Neural Networks for Enhanced Image Classification," \textit{IEICE Transactions on Information and Systems}, 2022. (under review)
    \end{rSubsection}

    \begin{rSubsection}{REFEREED CONFERENCES}{}{}{}{}
        \item \textbf{Naoya Muramatsu}*, Zico da Silva*, Daniel Joska, Fred Nicolls, Amir Patel, "Improving 3D Markerless Pose Estimation of Animals in the Wild using Low-Cost Cameras," in Proc. IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS 2022) (* co-first authors). (under review)
        \item Amaan Vally, Daniel Joska, \textbf{Naoya Muramatsu}, Paul Amayo, Amir Patel, "3D Markerless Motion Capture of Animals in the Wild using Autonomous Tracking Cameras," in Proc. IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS 2022). (under review)
        \item Daniel Joska, Liam Clark, \textbf{Naoya Muramatsu}, Ricky Jericevich, Fred Nicolls, Alexander Mathis, Mackenzie Mathis, Amir Patel, "AcinoSet: A 3D Pose Estimation Dataset and Baseline Models for Cheetahs in the Wild," in Proc. IEEE International Conference on Robotics and Automation (ICRA 2021).
        \item Chun Wei Ooi, \textbf{Naoya Muramatsu}, Yoichi Ochiai, "Eholo glass: Electroholography glass. A lensless approach to holographic augmented reality near-eye display," in Technical Briefs of 11th ACM SIGGRAPH Asia (SA 2018).
        \item Natsumi Kato*, Hiroyuki Osone*, Daitetsu Sato, \textbf{Naoya Muramatsu}, Yoichi Ochiai, "DeepWear: a Case Study of Collaborative Design between Human and Artificial Intelligence,"  in Proc. 12th ACM Twelfth International Conference on Tangible, Embedded, and Embodied Interaction (TEI 2018) (* co-first authors).
        \item Natsumi Kato, Hiroyuki Osone, Daitetsu Sato, \textbf{Naoya Muramatsu}, Yoichi Ochiai, "Crowd Sourcing Clothes Design Directed by Adversarial Neural Networks," in  Adjunct Proc. 31st Neural Information Processing Systems (NIPS 2017 Workshop).
        \item \textbf{Naoya Muramatsu}, Chun Wei Ooi, Yuta Itoh, Yoichi Ochiai, "DeepHolo: Recognizing 3D Objects using a Binary-weighted Computer-Generated Hologram," in Technical Briefs of 10th ACM SIGGRAPH Asia (SA 2017).
        \item Mose Sakashita, Yuta Sato, Ayaka Ebisu, Keisuke Kawahara, Satoshi Hashizume, \textbf{Naoya Muramatsu}, Yoichi Ochiai, "Haptic Marionette: Wrist Control Technology Combined with Electrical Muscle Stimulation and Hanger Reflex," in in Adjunct Proc. 10th ACM SIGGRAPH Asia (SA 2017 Posters).
        \item \textbf{Naoya Muramatsu}, Ooi Chun Wei, Takashi Miyazaki, "Development of High Performance Filter for Indoor Positioning System," in Proc. 5th IIAE International Conference on Intelligent Systems and Image Processing 2017 (ICISIP 2017).
        \item \textbf{Naoya Muramatsu}, Kazuki Ohshima, Ryota Kawamura, Ooi Chun Wei, Yuta Sato, Yoichi Ochiai, "Sonoliards: Rendering Audible Sound Spots by Reflecting the Ultrasound Beams," in Adjunct Proc. 30th ACM User Interface Software and Technology (UIST 2017 Adjunct).
    \end{rSubsection}

    % \begin{rSubsection}{INTERNATIONAL CONFERENCES (NOT REFEREED)}{}{}{}{}
    % \end{rSubsection}

    % \begin{rSubsection}{DOMESTIC CONFERENCES (REFEREED)}{}{}{}{}
    % \end{rSubsection}

    \begin{rSubsection}{NON-REFEREED CONFERENCES}{}{}{}{}
        \item \textbf{Naoya Muramatsu}, Hai-Tao Yu, "Combining Spiking Neural Network and Artificial Neural Network for Enhanced Image Classification," in Proc. 13th Data Engineering and Information Management (DEIM 2021).
        \item \textbf{Naoya Muramatsu}, Tetsuji Satoh, Takayasu Fushimi, "Product Attribute Extraction Method Based on Transition Pattern of Review Point of View," in Proc. 9th Data Engineering and Information Management (DEIM 2017). (Student Presentation Award) % レビュー観点の推移パターンに基づく商品属性の抽出手法
    \end{rSubsection}

\end{rSection}

\begin{rSection}{Professional Experience} \itemsep 4pt
    \begin{rSubsection}{PAPER REVIEWER}{}{}{}{}
        \item IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS), 2022.
        \item ACM Augmented Human International Conference (AH), 2018.
    \end{rSubsection}
    \begin{rSubsection}{PROFESSIONAL CERTIFICATES}{}{}{}{}
        \item Kinematics: Describing the Motions of Spacecraft (Coursera), University of Colorado Boulder, 2022.
        \item Motion Planning for Self-Driving Cars (Coursera), University of Toronto, 2021.
        \item Robotics: Mobility (Coursera), University of Pennsylvania, 2021.
        \item Julia Scientific Programming (Coursera), University of Cape Town, 2021.
        \item State Estimation and Localization for Self-Driving Cars (Coursera), University of Toronto, 2021.
        \item Visual Perception for Self-Driving Cars (Coursera), University of Toronto, 2021.
    \end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Fellowships}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{4ex}} l }
    2022    &   Incoming International Student Scholarship at University of Cape Town (35,000 ZAR) \\
            &   Electrical Engineering P/G Scholarship at University of Cape Town (20,000 ZAR) \\
    \end{tabular}
\end{rSection}

%----------------------------------------------------------------------------------------
% \begin{rSection}{Research Grants}
%     \begin{tabular}{ @{} >{\bfseries}l @{\hspace{4ex}} l }
%     \end{tabular}
% \end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Awards}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{4ex}} l }
    2019    &   \textbf{Super Creator} at MITOU Projects  \\
            &   (This award were given 16 creators from 27 people adopted from 300+ applications) \\
    2018    &   MITOU Projects (2,304,000 JPY) \\
    2018    &   \textbf{President's Award for Students} at University of Tsukuba  \\
    2017    &   \textbf{Student Presentation Award} at DEIM 2017   \\
    2015    &   \textbf{Third Prize} at RoboCupJunior Soccer 2015 (Hokushinetsu Block)  \\
    \end{tabular}
\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
    Programming Languages   &   Python(most fluent), MATLAB, Julia, C, C++, Verilog, \\
    & Shell Script, Ruby, JavaScript, SQL \\
    Machine Learning Libraries & Tensorflow, Keras, PyTorch, Scikit-learn, Chainer \\
    Software    &   Git, Docker, PyBullet, Pyomo, IPOPT, Processing, Autodesk Fusion360 \\
    OS          &   MacOS, Ubuntu, Windows, TrueNAS, CentOS \\
    Hardware    &   mbed, Arduino, Raspberry Pi, Hexapod \\
    \end{tabular}

\end{rSection}


%----------------------------------------------------------------------------------------
\begin{rSection}{Links}
    {\bf Portfolio} \hfill {\url{https://denden047.github.io/index_en.html}} \\
    {\bf GitHub} \hfill {\url{https://github.com/DenDen047}} \\
    {\bf Linkedin} \hfill {\url{https://www.linkedin.com/in/naoya-muramatsu-a01182184/}} \\
\end{rSection}

\end{document}
